---
title: "memor: Customizable LaTeX Template for rmarkdown"
author: Hao Zhu, Timothy Tsai, Thomas Travison
date: "`r Sys.Date()`"
output: 
  memor::pdf_memo:
    logo: "memor.png"
    logo_height: 2.5cm
    use_profile: false
    company:
      name: Institute for Aging Research
      address: 1200 Centre St, Boston, MA
      phone: 617-971-5386
      email: stats@hsl.harvard.edu
    confidential: false
    watermark: Open Access
    libertine: true
vignette: >
  %\VignetteIndexEntry{Sample Document}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
opts_chunk$set(warning = FALSE, message = FALSE, fig.pos = "h")
```

# Introduction
We love rmarkdown. In practice, however, we often have specific customization requirements for reporting of reproducible research. Some of these are universal, such as company logo or letterhead, contact info and so on. 

We created this `memor` package to allow for easier customization of `LaTeX`-based documents combining text and results from R. This document is produced using the following `YAML` header. Note that in this document, we are using the `Libertine` font, which can be enabled by setting `libertine: true`.

```
---
title: "memor: Customizable LaTeX Template for rmarkdown"
author: Hao Zhu, Timothy Tsai, Thomas Travison
date: "`r Sys.Date()`"
output: 
  memor::pdf_memo:
    logo: "memor.png"
    logo_height: 2.5cm
    use_profile: false
    company:
      name: Institute for Aging Research
      address: 1200 Centre St, Boston, MA
      phone: 617-971-5386
      email: stats@hsl.harvard.edu
    confidential: false
    watermark: Open Access
    libertine: true
---
```

# Installation
```{r, eval=FALSE}
install.packages("memor")

# For dev version
devtools::install_github("hebrewseniorlife/memor")
```

# Getting Started
Here are the list of options that is available in `memor`. As with the default `rmarkdown` template, not all need be specified. At the same time, it can also take all the other options from `rmarkdown::pdf_document`, such as `keet_tex`, `includes`, etc.
 
```
output: 
  memor::pdf_memo:
    use_profile: false
    logo: "logo.png"
    company: 
      name: Your company's name
      address: Your address
      phone: 888.888.8888
      email: your_email@email.com
    short_title: short title for page header
    watermark: (optional) watermark
    confidential: true
    libertine: false
    chinese: false
    logo_height: 1.2cm
    watermark_color: gray
    footer_on_first_page: true
    toc: false
    lot: false
    lof: false
    number_sections: true
    latex_engine: xelatex
```

In the interest of reducing the length of 'yaml' headers and allowing for standardization within teams, we have developed a mechanism that allows one to save one's configuration or "profile" in an isolated file, which can be reused for other reports and shared with colleagues. During the process of rendering, information saved in the profile file will be automatically pulled and used to generate the final document (but information defined in local environment will be used with priority). 

To better facilitate this process, we created a RStudio Addin to help you quickly locate the file. This addin does nothing but to open up the `~/memor-profile.yaml` file in your home directory (if this file doesn't exist, it will create one). Note that if you have a profile but you don't want to use the profile for certain document, you can disable this behavior by setting the `use_profile` option to `false.` Furthermore, if you are customizing the location of the profile file using the `memor_profile` option, which can be specified in a `.Rprofile`, so your group can put this file in a shared space. 