---
title: "memor: Customizable LaTeX Template for rmarkdown"
author: 
- Hao Zhu
- Timothy Tsai
- Thomas Travison
date: "`r Sys.Date()`"
output: 
  memor::pdf_memo:
    logo: "memor.png"
    logo_height: 2.5cm
    company:
      name: Institute for Aging Research
      address: 1200 Centre St, Boston, MA
      phone: 617-971-5386
      email: stats@hsl.harvard.edu
    confidential: true
    watermark: Not So Secret
---

```{r setup, include = FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
opts_chunk$set(warning = FALSE, message = FALSE)
```

# Introduction
We love rmarkdown. In practice, however, we often have specific customization requirements for reporting of reproducible research. Some of these are universal, such as company logo or letterhead, contact info and so on. 

We created this `memor` package to allow for easier customization of `LaTex`-based documents combining text and results from R. This document is produced using the following `YAML` header. 

```
title: "memor: Customizable LaTeX Template for rmarkdown"
author: 
- Hao Zhu
- Timothy Tsai
- Thomas Travison
date: "`r Sys.Date()`"
output: 
  memor::pdf_memo:
    logo: "memor.png"
    logo_height: 2.5cm
    company:
      name: Institute for Aging Research
      address: 1200 Centre St, Boston, MA
      phone: 617-971-5386
      email: stats@hsl.harvard.edu
    confidential: true
    watermark: Not So Secret
```

# Section 2
Here are the table and figure.
```{r}
kable(mtcars[1:5, 1:5], booktabs = T, caption = "a table") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "left")
```

```{r}
ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point()
```
