---
title: "memor: Customizable LaTeX Template for rmarkdown"
author: Hao Zhu, Timothy Tsai, Thomas Travison
date: "`r Sys.Date()`"
output: 
  memor::pdf_memo:
    keep_tex: true
    logo: "memor.png"
    logo_height: 2.5cm
    use_profile: false
    company:
      name: Institute for Aging Research
      address: 1200 Centre St, Boston, MA
      phone: 617-971-5386
      email: stats@hsl.harvard.edu
    confidential: false
    watermark: Open Access
---

```{r setup, include = FALSE}
library(knitr)
library(kableExtra)
library(ggplot2)
opts_chunk$set(warning = FALSE, message = FALSE, fig.pos = "h")
```

# Introduction
We love rmarkdown. In practice, however, we often have specific customization requirements for reporting of reproducible research. Some of these are universal, such as company logo or letterhead, contact info and so on. 

We created this `memor` package to allow for easier customization of `LaTeX`-based documents combining text and results from R. This document is produced using the following `YAML` header. 

```
---
title: "memor: Customizable LaTeX Template for rmarkdown"
author: Hao Zhu, Timothy Tsai, Thomas Travison
date: "`r Sys.Date()`"
output: 
  memor::pdf_memo:
    keep_tex: true
    logo: "memor.png"
    logo_height: 2.5cm
    company:
      name: Institute for Aging Research
      address: 1200 Centre St, Boston, MA
      phone: 617-971-5386
      email: stats@hsl.harvard.edu
    confidential: false
    watermark: Open Access
---
```

# Tables & Figures
Here are how tables and figures looks like in this template. Caption color is controlled by `citecolor`.
```{r}
kable(mtcars[1:5, 1:5], booktabs = T, caption = "A Table") %>%
  kable_styling(latex_options = c("striped", "HOLD_position"), position = "left")
```

```{r, fig.cap="A Plot", out.extra=""}
ggplot(mtcars, aes(x = mpg, y = wt)) +
  geom_point()
```
